Survey on Aspect-Based Sentiment Analysis

### 2023-04-16 paper/paper.tex
milestone 1

\documentclass[conference]{IEEEtran}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

@@

\section{Introduction}
An important area of study within the field of Natural Language Processing (NLP) is Sentiment Analysis (SA). SA is defined as extracting the emotional tone or the expressed polarity in a given text. This is usually done by classifying a given text as expressing a positive, a negative, or a neutral sentiment. A further area of study within SA is Feature-Based or Aspect-Based Sentiment Analysis (ABSA). This refers to the extraction of expressed sentiments about the individual entitities or objects within a text.

The motivation behind studying ABSA is simply that there is no scarcity in the amount of text containing opinions being produced. And it is very often too simplistic of an approach to deem an entire text as expressing a positive, negative, or neutral opinion. The reality is that within an opinion piece, the writer is usually expressing opinions regarding multiple different aspects or subjects which then build up to the overall opinion being expressed by the text. Though it is valuable to find out the overall opinion being expressed by a text, it is more actionable for a concerned entity of an opinion piece to be able to extract the opinions about the individual aspects mentioned within the text.

(Subtasks of Aspect extraction and aspect sentiment classification, should mention here?)

@@

The aim of this survey is to investigate the current state of ABSA and the latest techniques being employed to accomplish ABSA. The effectiveness, achievements, and the drawbacks of these techniques will also be explored so that we can clearly see the progress that has been made within this field of SA.

\section{Ignore everything below here, just a tamplate}

\subsection{Maintaining the Integrity of the Specifications}

The IEEEtran class file is used to format your paper and style the text. All margins, 
column widths, line spaces, and text fonts are prescribed; please do not 
alter them. You may note peculiarities. For example, the head margin
measures proportionately more than is customary. This measurement 
and others are deliberate, using specifications that anticipate your paper 
as one part of the entire proceedings, and not as an independent document. 
Please do not revise any of the current designations.

>>>>

\documentclass[conference]{IEEEtran}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

\begin{document}

@@

\section{Introduction}
An important area of study within the field of Natural Language Processing (NLP) is Sentiment Analysis (SA). SA is defined as extracting the emotional tone or the expressed polarity in a given text. This is usually done by classifying a given text as expressing a positive, a negative, or a neutral sentiment. A further area of study within SA is Feature-Based or Aspect-Based Sentiment Analysis (ABSA). This refers to the extraction of expressed sentiments about the individual entities or objects within a text.

The motivation behind studying ABSA is simply that there is no scarcity in the amount of text containing opinions being produced. And it is often too simplistic of an approach to deem an entire text as expressing a positive, a negative, or a neutral opinion. The reality is that within an opinion piece, the writer is usually expressing opinions regarding multiple different aspects or subjects which then build up to the overall opinion being expressed by the text. Though it is valuable to find out the overall opinion being expressed by a text, it is more actionable for a concerned entity of an opinion piece to be able to extract the opinions about the individual aspects mentioned within the text.

Two important subtasks in ABSA are Aspect Extraction (AE) and Aspect Sentiment Classification (ASC). These subtasks have been the point of focus in many studies pertaining to ABSA since their introduction in SemEval 2014, a research workshop on NLP. AE is the subtask in ABSA which focuses on extracting the objects from a given text regarding which a sentiment is being expressed while ASC is the subtask which focuses on classifying the expressed sentiment for each aspect that was extracted.

@@

The aim of this survey is to investigate the a small selection of papers from 4 time intervals and review those papers to ascertain the progress made in the field of ABSA.

\section{Paper Reviews}

\subsection{2020-2023}

\textit{\textbf{Adversarial Training for Aspect-Based Sentiment
Analysis with BERT, A. Karimi et al, 2020.}}

This paper talks about the idea of adversarial training, i.e. introducing noise or perturbations to input such that to a human it would seem as the same input with some noise but a neural network would persive that as a completely different input and may not classify it correctly. This approach has already been used for sentence classification but not in ABSA.

The models used in this paper is are extensions of the Bidirectional Encoder Representations from Transformers (BERT) model. The input sentences first go through a BERT word embedding layer to encode them. The encoded words are then passed through a BERT encoder following which their loss is calculated using a cross entropy loss function. After this the loss is used to calculate perturbations which are then added to the embeddings to produce input to attack the encoder and force it to give incorrect results. The adversarial loss and the normal loss are summed up to give the overall model loss, which is then minimized using backpropogation. A representation of this model is given by Figure 1. This model was used in both AE and ASC subtasks.

\begin{figure}[htbp]
\centerline{\includegraphics[keepaspectratio, width=0.45\textwidth]{pics/1.png}}
\caption{A representation of the model used by A. Karimi et al.}
\label{fig}
\end{figure}

\begin{figure*}
\centerline{\includegraphics[keepaspectratio, width=\textwidth]{pics/2.png}}
  \caption{A summary of the aims of Y. Qiang at al in this paper.}
\end{figure*}

For the AE subtask, the goal was to assign each word a label so as to specify whether it is the beginning of an aspect, inside an aspect or not in any aspect. For the ASC subtask, the output from the previous subtask is used as input (in the evaluation stage, while the actual true values are utilized in training) with the modification that each text is repeated as many times as there are aspects in it so that the setiment for each aspect can be classified separately.

The hyperparameter to be optimized is the variable that controls how big the perturbations being added to the input sample are. The challenge with optimizing that was that the adversarial sample to be produced needed to be similar enough to the input to be classified as the same but also different enough from the input so as to challenge the model. The issue that the authors faced is that they were using 2 distinct datasets but the best value that they found was different for both meaning that the dataset itself influences the best value for this parameter.

Furthermore, as the authors were buiding upon another research on the same topic but using a post-trained BERT (BERT-PT), they had to keep many things in their paper and methodology consistent with that approach. This means that their paper is easy to compare with other approaches but it seems there was still room for further experimentation for their approach as it was constrained so as to be comparable.

\begin{table}[htbp]
\caption{Results of the model produced by Y. Qiang et al.}
\begin{center}
\begin{tabular}{|c|c|c|c|}
\hline
\multicolumn{2}{|c|}{\textbf{Restaurant}} & \multicolumn{2}{|c|}{\textbf{Laptop}} \\
\hline
\textbf{AE} & \textbf{ASC} & \textbf{AE} & \textbf{ASC} \\
\hline
80.9 & 85.4 & 85.6 & 78.1 \\
\hline
\end{tabular}
\end{center}
\end{table}

The results were indeed an improvement upon BERT-PT and it can be said that they had produced the best results at the time for the given datasets.\\

\textit{\textbf{Toward Tag-free Aspect Based Sentiment Analysis:
A Multiple Attention Network Approach, Y. Qiang et al, 2020.}}

This paper identifies the issue that datasets for ABSA need to have the aspects tagged manually, which leads to their being less relevant data available even though there is a very large number of review and opinion texts available online today. This is refered to as the cold-start problem. They propose a new Multiple-Attention Network (MAN) approach which crawls the review data from review websites to extract the tag-free review text, aspect-level ratings, and overall ratings. Their aim is to provide an end-to-end automatic solution to perform ABSA as well as to uncover the weighted contribution of each word towards the aspect-level and overall polarities. A summary of their aim is provided by Figure 2.

The contributions of this work are combatting the cold-start for ABSA models by creating a means to produce datasets from review websites, providing 2 new datasets made from TripAdvisor, and including a means of inferring the overall sentiment from the aspect polarities by identifying the contribution of each aspect towards the overall score. The paper comments that a lot of ABSA approaches are built on SemEval Task5, and the authors want a greater use of the massive online review data being generated from e-commerce websites by alleviating the laborious process of manually tagging the available reviews.

\begin{figure}[htbp]
\centerline{\includegraphics[keepaspectratio, width=0.5\textwidth]{pics/3.png}}
\caption{A representation of the model used by Y. Qiang et al.}
\label{fig}
\end{figure}

The authors provide 2 datasets, one for hotel ratings and the other for restaurant ratings, which they have produced by scraping reviews from TripAdvisor. As shown in Figure 3, the MAN model consists of a number of modules. In the model, the sentences are embedded into word vectors those vectors are combined with their positional information. The input is then parsed into a Bi-LSTM to produce hidden states for each word. Self-attention is then performed to produce allignment vectors for each word for each aspect which are combined with the original hidden states to produce the context vectors for each word.

Position-aware self attention is also performed as words which are closer to an aspect will have more relevance to it usually. These arrays of vectors are also produced for each aspect. Thus we get another set of position-aware alignment vectors. These are combined with the context vectors to give the final representaions of the aspects which can then be classified. The classification is performed overall as well as on each aspect on a positive or negative class bases.

Several standard pre-processing techniques, such as lemmatization, stemming, stop word removal and tokenization are used so as to reduce the number of words and to make the process more efficient. Also, the attention scores are used to derive the more important aspects from a text, which is then used to give more weightage to it when calculating the overall polarity.

\begin{table}[htbp]
\caption{Results of the model produced by Y. Qiang et al.}
\begin{center}
\begin{tabular}{|c|c|c|c|}
\hline
\multicolumn{2}{|c|}{\textbf{Restaurant}} & \multicolumn{2}{|c|}{\textbf{Hotel}} \\
\hline
\textbf{ACC} & \textbf{Macro-F1} & \textbf{ACC} & \textbf{Macro-F1} \\
\hline
89.64±0.18 & 77.60±0.26 & 83.06±0.14 & 79.81±0.22 \\
\hline
\end{tabular}
\end{center}
\end{table}

From the results above we can see that the model produced sufficiently high accuracy given the fact that the input data was unstructured and scraped off from a review website. And this paper has been successful in addressing the cold-start problem which it aimed to solve. Furthermore, it has introduced a method to build end-to-end ABSA solutions for unstructured data, which without doubt will be expanded upon in the future.\\

\textit{\textbf{Aspect-based Sentiment Analysis with
Type-aware Graph Convolutional Networks and Layer Ensemble, Y. Tian et al, 2021.}}

This paper talks about a better way of using dependancy parsing in ABSA. Previous implementations have used dependancy graphs for text to assist in performing ABSA for that text, but only the dependancies have been paid attention to, not the exact type of dependancy among the words. Clearly some dependancies such as the one between a noun and a verb in a simple sentence are more important in ascertaining the polarity of an aspect within a text as compared with other dependancies that exist within that sentence. If all dependancies are treated equally, this will clearly be a disadvantageous for the model in performing ABSA.

Additionally, this paper claims that although previous Graph Convolutional Networks (GCNs) have learned relations using multiple layers, they only use the result from the most recent layer for ABSA which leads to some being lost because different contextual information is present in different layers in an ensemble.

This paper investigates a Type-Aware Graph Convolutional Network (T-GCN) with multiple layers incorporating both word relational information and dependancy type information so as to improve on the current approaches for ABSA. The overall architecture for their approach is given by Figure 4.

\begin{figure}[htbp]
\centerline{\includegraphics[keepaspectratio, width=0.5\textwidth]{pics/4.png}}
\caption{The overall representation of the model used by Y. Tian et al.}
\label{fig}
\end{figure}

First, given an input sentence, off-the-shelf toolkits are used to get the dependancy information. From this information an adjacency matrix is made to show the relation information of the dependancy graph, and relation matrix is made to show the type information, as shown in Figure 5. The sentence along with the provided aspect information is tokenized and then the resultant words are vectorized and put through a BERT to get the relevant attention information.

\begin{figure}[htbp]
\centerline{\includegraphics[keepaspectratio, width=0.5\textwidth]{pics/5.png}}
\caption{An illustration of how the type-aware graph is built and how each layer in the T-GCN processes the hidden states.}
\label{fig}
\end{figure}

The graph and the hidden states are then input to the T-GCN where a transition matrix is used to map the relations to their embeddings. For each edge, each layer in the T-GCN first combines the hidden vector with its relational embedding, then the results for the two words connected by the edge are combined and the weight of this edge is calculated. The trainable weight matrix for that layer is then used to produce the intermediate hidden state. Finally, the weight of the edge is applied to the hidden state, and a ReLU activation is performed to produce the hidden state output. This output is then the input for the next layer.

For each word, every layer incorporates information from its connected words into it, this means that multiple layers could learn longer and complex relations. This paper proposes to thus study this contextual information from all the layers using an Attentive Layer Ensemble (ALE). The hidden vectors from each layer are summed and averaged with respect to the number of aspect terms that were initially provided to provide an output from each layer. A weighted average of these output vectors is then taken which is the final output vector for ABSA.

A fully connected layer is then used to map this output vector to the number of classes and then softmax activation is applied to predict the output sentiment for the aspect.

The model showed better accuracy as compared to other famous studies operating on the same datasets. The authors also portrayed which exact studies were utilizing dependancy information in their comparision. It is interesting to note that most of the studies with higher performance were using dependancy information in some form. This points to the reasoning that exploring the direction of incorporating dependancy type information to improve ABSA models might be the direction to go in in the future. The authors have also provided evidence that usng T-GCN and ALE both have lead to some improvements in the accuracy of the models.

\subsection{2020-2023}
